### 2022-10-13 doc/manuscript/translocation.qmd
Describe requirements for Nature Communications journal
Minor edits to methods text

DNA samples were collected via buccal swabbing of xx-xx frogs from eight Bd-naive populations and seven recovering populations.
These populations represented a wide latitudinal range in the southern Sierra Nevada from northern Yosemite National Park to south of Sequoia National Park (Figure Sx), and the latitudinal range of the two population types was similar.

@@

>>>>

DNA samples were collected via buccal swabbing of xx-xx frogs from seven Bd-naive populations <!--# Dusy 10220 not included due to small sample size? --> and seven recovering populations.
These populations represented a wide latitudinal range in the southern Sierra Nevada from northern Yosemite National Park to south of Sequoia National Park (Figure Sx), and the latitudinal range of the two population types was similar.

@@

Nature Communications

-   Article

    -   Papers published by the journal represent important advances of significance to specialists within each field.

    -   The main text (not including abstract, Methods, References and figure legends) is limited to 5,000 words. The maximum title length is 15 words.
